Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-07 Manuscript_analyses.Rmd
sensitivity analysis

histo<-ggplot(data=farm5_emissions$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~density~of~milk~production~(~kg~CO[2]*'-eq'~kg^-1)))

@@

ggsave("Fig_3_emission_density_farm5.png",width=5,height=3)

@@

## Population-wide emission density of milk production

Since the emission density of each household thus involves considerable uncertainty, such uncertainty should also be expected at the population level.

@@

ggsave("Fig_7_emission_density_all_farms.png")

@@

ggplot(data=slices, aes(Values, fill=Level)) +
 geom_density(alpha=.2) +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~of~milk~production~at~specific~milk~yield~per~capita~(kg~CO[2]*'-eq'~kg^-1))) + labs(fill='Production level') + theme_bw()

ggsave("Fig_8_emission_density_all_farms.png", width=7,height=5)

@@

@@

* considerable uncertainty in inputs to IPCC equations
* cause major uncertainty in emissions intensity estimates
* this makes it difficult to evaluate the emissions intensity of dairy farms in Kenya based on their milk yield alone - large differences are needed to be certain that one farm is more emissions-efficient than another one
* interventions clearly impact emissions intensity
* emissions intensity savings are substantial for all interventions, but still relatively small in comparison to the overall uncertainty associated with limited knowledge about values of input variables.
* it seems likely that a milk yield-based emissions reduction scheme might miss measures taken by farmers, at least if the reward scheme wants to be really sure that emissions reductions have in fact occurred.
* it seems the information content in milk yields isn't sufficient to base mitigation reward schemes on them
* might be a better idea after all to observe farmers' practices - did they implement any measures? Then they should be rewarded
* maybe rewarding measures taken is a better idea than evaluating emissions intensity based on milk yield alone.

# some remaining notes

For each slice, and each level of confidence, calculate the percentage of farms that made changes that would be correctly rewarded vs. the ones that did not change (the baseline population). Make a figure showing the Type I and Type II errors resulting from each confidence level at each baseline yield.

>>>>

histo<-ggplot(data=farm5_emissions$y, aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emissions~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^-1)))

@@

ggsave("Fig_3_emissions_intensity_farm5.png",width=5,height=3)

@@

## Population-wide emissions intensity of milk production

Since the emissions intensity of each household thus involves considerable uncertainty, such uncertainty should also be expected at the population level.

@@

ggsave("Fig_7_emissions_intensity_all_farms.png")

@@

ggplot(data=slices, aes(Values, fill=Level)) +
 geom_density(alpha=.2) +
  ylab("Relative probability") +
    xlab(expression(Emissions~intensity~of~milk~production~at~specific~milk~yield~per~capita~(kg~CO[2]*'-eq'~kg^-1))) + labs(fill='Production level') + theme_bw()

ggsave("Fig_8_emissions_intensity_all_farms.png", width=7,height=5)

@@

# Sensitivity analysis - which uncertainties matter?

To identify influential variables in the population that are particularly strongly related to emissions intensity, we can use the statistical procedure of Projection-to-Latent-Structures (PLS) regression. Based on the Variable-Importance-in-the-Projection (VIP) score, we can see, for which uncertain variables knowledge gains would be particularly fruitful.

pls_GHG<-dairy_households
pls_GHG$x<-pls_GHG$x[,which(!colnames(pls_GHG$x)=="Scenario")]

pls_out<-plsr.mcSimulation(object=pls_GHG, resultName = "CO2eq_per_milk")

legend_table<-read.csv("data/legend.csv", fileEncoding = "UTF-8-BOM")

plot_pls(pls_out,input_table=legend_table)
ggsave("Fig_25_PLS_dairy_households.png", width=8,height=5)
```

@@

* considerable uncertainty in inputs to IPCC equations
* cause major uncertainty in emissions intensity estimates
* this makes it difficult to evaluate the emissions intensity of dairy farms in Kenya based on their milk yield alone - large differences are needed to be certain that one farm is more emissions-efficient than another one
* interventions clearly impact emissions intensity
* emissions intensity savings are substantial for all interventions, but still relatively small in comparison to the overall uncertainty associated with limited knowledge about values of input variables.
* it seems likely that a milk yield-based emissions reduction scheme might miss measures taken by farmers, at least if the reward scheme wants to be really sure that emissions reductions have in fact occurred.
* it seems the information content in milk yields isn't sufficient to base mitigation reward schemes on them
* might be a better idea after all to observe farmers' practices - did they implement any measures? Then they should be rewarded
* maybe rewarding measures taken is a better idea than evaluating emissions intensity based on milk yield alone
* sensitivity analysis highlights the need to gain more clarity on milk yields - we specified a 90% confidence interval of mean +- 27.5%
* Improving reliability of milk yield measurements might make this indicator more viable

# Remaining jobs

- Feed intervention (how exactly?)
- Select what to present in the manuscript and the supplement
